A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-13 docs/icccn2009/paper.tex
Add OSGi section
git-svn-id: svn://localhost/netbeams/trunk@381 559edde2-a4d4-44e0-96fc-4035e40d7396

>>>>

\subsection{OSGi}

OSGi \cite{osgi} is a generic platform for "dynamic module system for Java\texttrademark".
\cite{Mueller07} used OSGi as platform their sensor network.
In \cite{Baude07} OSGi is used to support large scale deployment. OSGi is flexible
enough to be used in mobile devices and in application servers. One aspect not addressed
by OSGi is distributed communication (although some extensions have
been proposed,e.g., \cite{Rellermeyer}). DSP was designed to handle remote communication and,
therefore, can complement OSGi capability. DSP Components are OSGi bundles (in fact, DSP itself
is a bundle) and can be remotely and dynamically maintained. OSGi capabilities along with DSP
design make well suitable for our project.
